### 2014-04-09 brains-protocol.tex
Rework variable correlation part

\begin{itemize}
    \item \textbf{Centrality} $k$, measured by the number of incoming edges to a given node, i.e. the number of cues for which a given word is triggered as an association, which strongly relates to word polysemy.
    Note that in the present case, there is a quasi-perfect correlation between node incoming degree and node \emph{pagerank}~\citep{Page99}, a measure which had already been used by~\citet{Griffiths07} and which may be interpreted as a generalized and recursive measure of word polysemy: central nodes in the pagerank sense are words often selected as targets when presented with cues themselves often selected as targets, and so on recursively.
    \item \textbf{Clustering coefficient} $c$, which measures the extent to which a node belongs to a local aggregate of tightly connected nodes, and defined as the ratio between the number of actual v. possible edges between a node's neighbours \cite{watt-coll}.
    We compute the clustering coefficient on the undirected version of the FA network; we thus measure if a word belongs more or less to a local aggregate of equivalent words (from a ``free association'' point of view).
    \item \textbf{Betweenness coefficient} $b$, another measure of node centrality describing the extent to which a node tends to connect otherwise remote areas of the network~\citep{free:set}.
    More technically, it corresponds to the normalized number of shortest paths connecting dyads which pass through that node; the higher the coefficient, the more important that node is in ensuring the connectedness of the rest of the network.
    This quantity tells us if some words behave like unavoidable waypoints on the path associating one word to another.
\end{itemize}

@@

An important question here relates to the various possible correlations between all the variables we consider.

The age of acquisition is a key variable, primarily as a usual suspect in psycholinguistic studies, and also appears to be generally correlated to many of the other variables.
This relates to an ongoing debate suggesting that age of acquisition encodes a variety of phenomena which are difficult to disentangle from more specific phenomena, which could be captured by more independent variables such as \CN.
\rk{What do we conclude of that? Nuance results with AoA?}
\TB{Indeed, the minimal linear correlation of $aoa$ ($-0.31$) with other variables has a higher magnitude than the maximal linear correlation of other variables with each other ($-0.26$).}
\rk{how do we get to that conclusion?}

Additionally, number of phonemes and number of syllables exhibit a strong linear correlation ($0.85$).
The analysis showed a better prediction effect of number of phonemes over number of syllables, which is consistent with~\citet{nick-diss}, and we therefore chose to focus the presented results on the former only.
\rk{Rather, graphs are much nicer with number of phonemes than number of syllables: clearer tendencies, more data (there's holes with number of syllables). But not a prediction (prediction of what?)}

\bigskip
Network properties, finally, appear to be relatively weakly correlated with each other, across one network or between both networks (i.e. nodes with high index values are generally distinct between FA and WN).
We chose to focus the results on FA as this network presents a direct psychological interpretation (that human copy-pasting may or may not show the same type of trend as human free association), noting that prediction results are matched against WN as well.
\rk{comment peut-on dire que les nœuds importants dans FA ne sont pas nécessairement importants dans WN mais que, pourtant, la forme de la prédiction est la même? cela me semble illogique en première lecture}
\rk{Check those assertions}

\begin{figure}[!th]
    \includegraphics[width=\linewidth]{images/computed-figures/feature_correlations-filter1.png}
    \caption{Variable correlations \rk{rebuild with the variables we talk about and keep}}
\end{figure}

>>>>

\begin{itemize}
    \item \textbf{Centrality} $k$, initially measured by the number of incoming edges to a given node, i.e. the number of cues for which a given word is triggered as an association, which strongly relates to word polysemy.
    However in the present case there is a quasi-perfect correlation between node incoming degree and node \emph{pagerank}~\citep{Page99}, which will lead us to favour the latter later on. Word pagerank on the FA network had already been used by~\citet{Griffiths07}; it may be interpreted as a generalized and recursive measure of word polysemy: central nodes in the pagerank sense are words often selected as targets when presented with cues themselves often selected as targets, and so on recursively.
    \item \textbf{Clustering coefficient} $c$, which measures the extent to which a node belongs to a local aggregate of tightly connected nodes, and defined as the ratio between the number of actual v. possible edges between a node's neighbours \cite{watt-coll}.
    We compute the clustering coefficient on the undirected version of the FA network; we thus measure if a word belongs more or less to a local aggregate of equivalent words (from a ``free association'' point of view).
    \item \textbf{Betweenness coefficient} $b$, another measure of node centrality describing the extent to which a node tends to connect otherwise remote areas of the network~\citep{free:set}.
    More technically, it corresponds to the normalized number of shortest paths connecting dyads which pass through that node; the higher the coefficient, the more important that node is in ensuring the connectedness of the rest of the network.
    This quantity tells us if some words behave like unavoidable waypoints on the path associating one word to another.
\end{itemize}

@@

There is an important questions here about the possible correlations between all the variables we consider.

\begin{figure}[!th]
    \centering
    \includegraphics[width=\linewidth]{images/computed-figures/feature_correlations-filter1.png}
    \caption{Correlations in the initial set of features \rk{show non log version?}}
    \label{fig:feature-corrs-initial}
\end{figure}

Age of acquisition is a key variable which appears as a usual suspect in psycholinguistic studies and is also usually correlated to many of the other variables.
This relates to an ongoing debate suggesting that age of acquisition encodes a variety of phenomena, difficult to disentangle from more specific phenomena which could be captured by more independent variables such as~\CN{}.
Here however, as can be seen in Figure~\ref{fig:feature-corrs-initial}, age of acquisition has a relatively low correlation to the other variables (absolute value not above $0.42$ if we exclude the centrality measures), leading us to keep the variable in the rest of the analysis.

Number of phonemes and number of syllables naturally exhibit a strong linear correlation ($0.83$).
The analysis showed a better prediction effect of number of phonemes over number of syllables, which is consistent with~\citet{nick-diss}, and we therefore chose to focus the presented results on the former only.

Frequency and number of meanings both have relatively low levels of correlation to the other variables; we therefore also keep them in the rest of the analysis.

\bigskip
Network properties, on the other hand, are strongly dependant on one another.
As mentioned earlier, word degree and word pagerank have a very strong correlation ($0.89$) and, degree being generally more correlated to other variables, we chose to remove this variable from the results presented.
Finally betweenness centrality also exhibits strong correlation levels to the other network properties ($0.62$, $0.64$, and $0.72$ in absolute value), leading us to drop this final feature due to its redundancy.

The final set of variables we consider, as well as their cross-correlations, can be seen in Figure~\ref{fig:feature-corrs-filtered}.

\begin{figure}[!th]
    \centering
    \includegraphics[width=0.788\linewidth]{images/computed-figures/feature_correlations-filter2.png}
    \caption{Correlations in the filtered set of features \rk{show non log version?}}
    \label{fig:feature-corrs-filtered}
\end{figure}
